Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-17 paper/lostanlenRelevanceScattering.tex
re-organize supplementary material

\section{Supplementary material}

Time reversal of a real signal $\boldsymbol{x}(t)$ is equivalent
to the complex conjugation of its Fourier transform $\boldsymbol{\widehat{x}}(\omega$).
As a consequence, the Fourier transform modulus $\vert\boldsymbol{\widehat{x}}(\omega)\vert$
is not only invariant to translation, but also invariant to time reversal.
Yet, although invariance to translation is needed for classification,
invariance to time reversal is an undesirable property.
A simple way to break invariance to time reversal is to choose $\boldsymbol{\psi}(t)$
as an asymmetric wavelet instead of a Gabor symmetric wavelet.

@@

With the aim of building a pseudo-analytic admissible Gammatone wavelet,
\cite{Venkitaraman2014} have modified the definition of the Gammatone
auditory filter, by replacing the real-valued sine wave $\cos(2\pi t)$
by its analytic part $\exp(2\pi\mathrm{\mathrm{i}}t)$ and by taking
the first derivative of the gamma distribution, thus ensuring null
mean. The definition of the Gammatone wavelet becomes
\[
\boldsymbol{\psi}(t)=\left(2\pi(\mathrm{i}-\sigma)t^{N-1}+(N-1)t^{N-2}\right)\exp(-2\pi\sigma t)\exp(2\pi\mathrm{i}t)
\]
in the time domain, and
\[
\boldsymbol{\widehat{\psi}}(\omega)=\dfrac{\mathrm{i}\omega\times(N-1)!}{(\sigma+\mathrm{i}(\omega-\sigma))^{N}}
\]
in the Fourier domain. Besides its biological plausibility, the Gammatone
wavelet enjoys a near-optimal time-frequency localization with respect
to the Heisenberg uncertainty principle. Furthermore, this time-frequency
localization tends to optimality as $N$ approaches infinity, because
the limit $N\rightarrow+\infty$ yields a Gabor wavelet \cite{Cohen1995}.
Last but not least, the Gammatone wavelet transform of finite order
$N$ is causal, as opposed to the Morlet wavelet transform, which
makes it better suited to real-time applications. From an evolutionary
point of view, it has been argued that the Gammatone reaches a practical
compromise between time-frequency localization and causality constraints.
\cite{Venkitaraman2014} did not provide a formula for deducing $\sigma$
from the specification of a quality factor $Q$.
In this appendix, we provide a rationale for choosing the topmost center frequency $\xi$ of a Gammatone wavelet filter bank in a discrete-time setting. Then, we relate the bandwidth parameter $\sigma$ to the choice of a quality factor Q.

>>>>

\section{Supplementary material: }

The introductory paper on Gammatone wavelet \cite{Venkitaraman2014} does not provide a formula for deducing $\sigma$ from the specification of a quality factor $Q$.

In this appendix, we provide a rationale for choosing the topmost center frequency $\xi$ of a Gammatone wavelet filter bank in a discrete-time setting. Then, we relate the bandwidth parameter $\sigma$ to the choice of a quality factor Q.

\subsubsection*{Motivation}
Time reversal of a real signal $\boldsymbol{x}(t)$ is equivalent
to the complex conjugation of its Fourier transform $\boldsymbol{\widehat{x}}(\omega$).
As a consequence, the Fourier transform modulus $\vert\boldsymbol{\widehat{x}}(\omega)\vert$
is not only invariant to translation, but also invariant to time reversal.
Yet, although invariance to translation is needed for classification,
invariance to time reversal is an undesirable property.
A simple way to break invariance to time reversal is to choose $\boldsymbol{\psi}(t)$
as an asymmetric wavelet instead of a Gabor symmetric wavelet.

@@

\subsubsection*{Related work}

With the aim of building a pseudo-analytic admissible Gammatone wavelet,
\cite{Venkitaraman2014} have modified the definition of the Gammatone
auditory filter, by replacing the real-valued sine wave $\cos(2\pi t)$
by its analytic part $\exp(2\pi\mathrm{\mathrm{i}}t)$ and by taking
the first derivative of the gamma distribution, thus ensuring null
mean. The definition of the Gammatone wavelet becomes
\[
\boldsymbol{\psi}(t)=\left(2\pi(\mathrm{i}-\sigma)t^{N-1}+(N-1)t^{N-2}\right)\exp(-2\pi\sigma t)\exp(2\pi\mathrm{i}t)
\]
in the time domain, and
\[
\boldsymbol{\widehat{\psi}}(\omega)=\dfrac{\mathrm{i}\omega\times(N-1)!}{(\sigma+\mathrm{i}(\omega-\sigma))^{N}}
\]
in the Fourier domain. Besides its biological plausibility, the Gammatone
wavelet enjoys a near-optimal time-frequency localization with respect
to the Heisenberg uncertainty principle. Furthermore, this time-frequency
localization tends to optimality as $N$ approaches infinity, because
the limit $N\rightarrow+\infty$ yields a Gabor wavelet \cite{Cohen1995}.
Last but not least, the Gammatone wavelet transform of finite order
$N$ is causal, as opposed to the Morlet wavelet transform, which
makes it better suited to real-time applications. From an evolutionary
point of view, it has been argued that the Gammatone reaches a practical
compromise between time-frequency localization and causality constraints.

\subsubsection*{Center frequency parameter}
